### 2014-05-27 examples/fsr.rmd
add Sen's code for t likelihood

```{r}
set.seed(100)
library(ashr)
library(qvalue)
n = 10000
beta = rnorm(n)
sebetahat = 1
betahat = beta + rnorm(n,0,sebetahat)

@@

```{r}
  hist(p,prob=TRUE)
  abline(h=z.qvalue$pi0,lwd=2)
  text(0.95, z.qvalue$pi0+0.06, "pi0 (q value)")
  abline(h=get_pi0(z.ash),col=2,lwd=2)
  text(0.95, get_pi0(z.ash)+0.06,"pi0 (ash)",col=2)
```

>>>>

```{r}
opts_chunk$set(fig.path='figure/lfsr/')
set.seed(100)
library(ashr)
library(qvalue)
n = 10000
beta = rnorm(n)
sebetahat = 1
betahat = beta + rnorm(n,0,sebetahat)

@@

```{r, }
  hist(p,prob=TRUE)
  abline(h=z.qvalue$pi0,lwd=2)
  text(0.95, z.qvalue$pi0+0.06, "pi0 (q value)")
  abline(h=get_pi0(z.ash),col=2,lwd=2)
  text(0.95, get_pi0(z.ash)+0.06,"pi0 (ash)",col=2)
```
